Semi-permeable vesicles: mathematical formulation, numerics and physics

### 2020-05-11 vesicle_code/docs/permeableVes/main.tex
worked on shear example

\newif\ifTikz
\Tikztrue

@@

@@

In addition to computing the steady shape, we can compute the transient
area of the vesicle. Parameterizing the vesicle with $\xx$, its area is
\begin{align}
  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds .
\end{align}
The derivative of $A(t)$ includes terms due to the time derivative of
$\xx \cdot \nn$, and a term due to interface
stretching~\cite{lai-tse-hua2008}. However, the stretching term is zero
because of the local inextensibility condition. Therefore,
\begin{align}
  \dot{A}(t) &= \frac{1}{2} \int_{\gamma} \pderiv{}{t} 
    (\xx \cdot \nn) \, ds = 
  \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
  \frac{1}{2} \int_{\gamma} (\xx \cdot \dot{\nn})\, ds.
\end{align}
The second integrand can be computed as
\begin{align}
  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
\end{align}
Therefore,
\begin{align}
  \dot{A}(t) &= \int_\gamma (\dot{\xx} \cdot \nn)\, ds 
  = \int_\gamma \left(\beta (\ff \cdot \nn)\nn + \SS[\ff]\right) 
      \cdot \nn\, ds 
  = \beta \int_\gamma (\ff \cdot \nn)\, ds,
\end{align}
where the last equality follows from the incompressibility of the
single-layer potential and the divergence theorem.  Using integration by
parts and the Frenet-Serret identities, we have
\begin{align}
  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
    \right) \cdot \kappa \xx_s \, ds \\
  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
    \, ds \\
  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
    \, ds.
\end{align}
Finally, using the relationship between the Lagrange multiplier
$\sigma$, and the tension $\Lambda$, the area of a semi-permeable
vesicle is governed by
\begin{align}
  \dot{A}(t) = \beta \int_\gamma \left(
    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
  \label{eqn:areaROC}
\end{align}
Note that this is consistent with the steady state curvature and
tension~\eqref{eqn:SSshape} since these constant values result in the
integrand in equation~\eqref{eqn:areaROC} being zero.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples}
We consider a single semi-permeable vesicle in four different flow
regimes. All vesicles have a length of $L=4\pi$, but the area is not
conserved because of semi-permeability. However, the area is bounded
above by the area of a circle with circumference $L=4\pi$. Therefore,
$A(t) \leq 4\pi \approx 12.56$ for all simulations. For each simulation,
we use an adaptive second-order time stepping method~\cite{qua-bir2016}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quiescent Flow} 
We start by considering a semi-permeable vesicle in a quiescent flow.
For an impermeable vesicle, the vesicle relaxes to a steady-state shape
with negative and constant tension~\cite{kra-win-sei-lip1996}. However,
from equation~\eqref{eqn:SSshape}, we know that a semipermeable vesicle
will relax to a circle with positive constant tension. Since the area of
a semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, we expect
that the time to reach steady state, and the time required for a small
amount of inflation, both scale with $\beta^{-1}$. We simulate a vesicle
with initial reduced area $0.65$ with several values of $\beta$.  In
Table~\ref{tbl:ellipseRelaxTimes}, we report the time, $t_\mathrm{SS}$,
required for the vesicle's area to be within 1.3\% of its maximum area,
and the time, $t_\mathrm{SP}$, required for the vesicle's area to exceed
1.3\% of its initial area. We see that both these time scales do scale
with $\beta^{-1}$. In Figure~\ref{fig:ellipseArea}, we plot the area of
a vesicle with different permeability rates. The area is computed
directly from the vesicle shape (solid lines) and by integrating
equation~\eqref{eqn:areaROC} (marks) with a first-order method. We also
include black dashed lines indicating the times, $t_{\mathrm{SS}}$, that
the vesicle is near its steady state circular shape.

\begin{table}[htp]
  \centering
  \begin{tabular}{|C{2cm}C{3cm}C{3cm}C{3cm}C{3cm}|}
    \hline
    $\beta$ & $t_\mathrm{SS}$ & ratio & $t_\mathrm{SP}$ & ratio \\
    \hline
    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
              & $2.17 \times 10^{-2}$ & --- \\ 
    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
                $1.25 \times 10^{-1}$ & 5.76 \\
    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
                $1.59 \times 10^{0}$ & 12.72 \\
    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
                $2.19 \times 10^{1}$ & 13.77 \\
    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
                $2.14 \times 10^{2}$ & 9.77 \\
    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
                $2.20 \times 10^{3}$ & 10.14 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
  vesicle to reach relaxation time ($t_\mathrm{SS}$) and to begin
  inflating ($t_\mathrm{SP}$).}
\end{table}

\begin{figure}[htp]
\centering
\ifTikz
\input{figures/ellipseArea.tikz}
\fi
  \caption{\label{fig:ellipseArea} The area of an elliptical
  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
  flow. The solid lines compute the area directly from the vesicle
  shape, while the marks are computed by integrating
  equation~\eqref{eqn:areaROC}. The dashed black lines are the times
  when the vesicle's area is within 1\% of its maximum value of $4\pi$.}
\end{figure}

We further analyze the transient dynamics for small $\beta$ by
considering the contribution of each term in~\eqref{eqn:vesVelocity} to
the vesicle velocity. Initially, the semi-permeability term $\beta(\ff
\cdot \nn)\nn$ is much smaller than the velocity due to the force
balance $\SS[\ff]$. Therefore, the velocity resembles that of an
impermeable vesicle. However, as the vesicle approaches the impermeable
limit, the velocity contribution from the force balance decays below the
contribution from semi-permeability, and we expect the vesicle to begin
inflating due to permeability. In Figure~\ref{fig:vesVelocity}, we plot
the velocities at three times due to force balance (blue) and
semi-permeability (red), where $\beta = 10^{-3}$. We also plot the
velocity of an identically initialized impermeable vesicle. At $t=0.5$,
the velocity due to semi-permeability is small relative to the velocity
due to force balance, and the semi-permeable vesicle velocity matches
with the impermeable vesicle velocity. At time $t=5$, the impermeable
vesicle is near its steady state shape, and its velocity is comparable
to the semi-permeable velocity, so the vesicle's area begins to
increase. Then, at time $t=50$, the impermeable vesicle is at its steady
state, while the semi-permeable vesicle still has contributions due to
semi-permeability and force balance. In
Figure~\ref{fig:vesVelocityNorm}, we plot the max norm of the different
velocity contributions as a function of time. The black dashed lines
correspond to the times reported in Figure~\ref{fig:vesVelocity}. Again,
we see that the velocity of a semi-permeable vesicle is initially agrees
with the velocity of an impermeable vesicle. Then, as the velocity due
to force balance approaches zero, the semi-permeable term becomes
significant, causing the vesicle to inflate until it reaches a circular
shape.

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/ellipseVelocity1.tikz}
  \input{figures/ellipseVelocity2.tikz}
  \input{figures/ellipseVelocity3.tikz}
  \fi
  \caption{\label{fig:vesVelocity} The velocity contributions due to
  semi-permeability (red) and force balance (blue). The green dashed
  line is the velocity of an impermeable vesicle with an identical
  initial shape.}
\end{figure}

@@

Finally, we consider a semi-permeable vesicle with initial regions of
positive and negative curvature. The permeability rate is $\beta=1$, and
several time steps are illustrated in Figure~\ref{fig:starShape}. As
expected, the steady state shape is circular. The vesicle undergoes
three general behaviors: (i) for $t \in (0,1.6 \times 10^{-2})$, the
vesicle has a net negative flux resulting in a loss of area; (ii) for $t
\in (1.6 \times 10^{-2},1.0 \times 10^{0})$, the vesicle has a net
positive flux and the tension most of the membrane is undergoing
negative tension; (iii) for $t \in (1.0 \times 10^{0},2.0 \times
10^{0})$, the vesicle is near its steady state and transitions to a
positive constant tension.

We compute the tension $\Lambda$ and the flux $(-\xx_{ssss} + (\sigma
\xx_s)_s) \cdot \nn$ and plot the results in
Figure~\ref{fig:starTensionFlux}.  In the first time interval, the
vesicle deflates. Near the points of largest negative curvature, there
is a large negative tension and large inflow (positive flux).
Correspondingly, near the points with largest positive curvature, there
is a small tension and outflow (negative flux). In the second time
interval, the tension is negative and the flux is positive nearly
everywhere. The regions of large negative curvature correspond to
regions with the largest negative tension and the most inflow. Finally,
in the last time interval, the tension transitions to a positive
constant function, the flux transitions to zero, and the result is a
steady state circular vesicle with positive constant tension.

\begin{figure}[htp]
    \ifTikz
    \input{figures/starRelaxation1.tikz}
    \quad
    \input{figures/starRelaxation2.tikz}
    \quad
    \input{figures/starRelaxation3.tikz}
    \quad
    \input{figures/starRelaxation4.tikz}
    \quad
    \input{figures/starRelaxation5.tikz}
    \fi
  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
  steps are not equispaced.}
\end{figure}

@@

  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
  flux (bottom) of the semi-permeable vesicle in quiescent
  flow with $\beta=1$.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear Flow}
\begin{itemize}
  \item Never goes to a circle
  \item Area formula works
  \item Mild dependence on initial shape
  \item Most slender tank treading shapes seen for small $\beta$ and
    large $\chi$

  \item Look at tank-treading angle, tank-trading speed, reduced area,
    absolute value of the permeable flux
  \item Max flux at the steady state as a function of beta and
    $\dot{\gamma}$

@@

We consider a semi-permeable vesicle in the shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$. For impermeable vesicles,
depending on the reduced area and viscosity contrast, the vesicle will
either tumble or tank-tread~\cite{fin-lam-sei-gom2008}. Since we are
considering permeable vesicles, we assume that there is no fluid
viscosity.

%\ifTikz
%\input{figures/shearPhaseDiagram.tikz} 
%\fi

>>>>

\newif\ifTikz
\Tikztrue
%\Tikzfalse

@@

Reduced area is $\nu = 4\pi A/L^2$.

@@

In addition to computing the steady shape, we can compute the transient
area of the vesicle. Parameterizing the vesicle with $\xx$, its area is
\begin{align}
  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds .
  \label{eqn:area}
\end{align}
The derivative of $A(t)$ includes terms due to the time derivative of
$\xx \cdot \nn$, and a term due to interface
stretching~\cite{lai-tse-hua2008}. However, the stretching term is zero
because of the local inextensibility condition. Therefore,
\begin{align}
  \dot{A}(t) &= \frac{1}{2} \int_{\gamma} \pderiv{}{t} 
    (\xx \cdot \nn) \, ds = 
  \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
  \frac{1}{2} \int_{\gamma} (\xx \cdot \dot{\nn})\, ds.
\end{align}
The second integrand can be computed as
\begin{align}
  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
\end{align}
Therefore,
\begin{align}
  \dot{A}(t) &= \int_\gamma (\dot{\xx} \cdot \nn)\, ds 
  = \int_\gamma \left(\beta (\ff \cdot \nn)\nn + \SS[\ff]\right) 
      \cdot \nn\, ds 
  = \beta \int_\gamma (\ff \cdot \nn)\, ds,
\end{align}
where the last equality follows from the incompressibility of the
single-layer potential and the divergence theorem.  Using integration by
parts and the Frenet-Serret identities, we have
\begin{align}
  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
    \right) \cdot \kappa \xx_s \, ds \\
  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
    \, ds \\
  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
    \, ds.
\end{align}
Finally, using the relationship between the Lagrange multiplier
$\sigma$, and the tension $\Lambda$, the area of a semi-permeable
vesicle is governed by
\begin{align}
  \dot{A}(t) = \beta \int_\gamma \left(
    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
  \label{eqn:areaROC}
\end{align}
Note that this is consistent with the steady state curvature and
tension~\eqref{eqn:SSshape} since these constant values result in the
integrand in equation~\eqref{eqn:areaROC} being zero.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples}
We consider a single semi-permeable vesicle in four different flow
regimes. All vesicles have a length of $L=4\pi$, but the area is not
conserved because of semi-permeability. However, the area is bounded by
$4\pi$ which is the area of a circle with length $L=4\pi$. For each
simulation, we apply an SDC second-order adaptive time stepping
method~\cite{qua-bir2016}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quiescent Flow} 
We consider a semi-permeable vesicle with initial reduced area $0.65$
and several different permeability rates $\beta$ in a quiescent flow. If
the vesicle is impermeable, meaning that $\beta = 0$, it will relax to a
steady-state shape with negative and constant
tension~\cite{kra-win-sei-lip1996}. However, from
equation~\eqref{eqn:SSshape}, a semipermeable vesicle relaxes to a
circle with positive constant tension. Since the area of a
semi-permeable vesicle is governed by~\eqref{eqn:areaROC}, we expect
that the time for the vesicle to deviate from its initial area, and the
time to reach the steady state will both scale with $\beta^{-1}$. In
Figure~\ref{fig:ellipseArea}, we plot the area of a vesicle with
different permeability rates. The area is computed directly from the
vesicle shape (solid lines) and by integrating
equation~\eqref{eqn:areaROC} (marks) with a first-order method. We also
include black dashed lines indicating the times, $t_{\mathrm{steady}}$,
that the vesicle is near its steady state circular shape. In
Table~\ref{tbl:ellipseRelaxTimes}, we report the time,
$t_\mathrm{steady}$, required for the vesicle's area to be within 1.3\%
of its maximum area, and the time, $t_\mathrm{inflate}$, required for
the vesicle's area to exceed 1.3\% of its initial area. We see that both
times scale with $\beta^{-1}$.

\begin{table}[htp]
  \centering
  \begin{tabular}{|C{2cm}C{3cm}C{3cm}C{3cm}C{3cm}|}
    \hline
    $\beta$ & $t_\mathrm{steady}$ & ratio & $t_\mathrm{inflate}$ & ratio \\
    \hline
    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
              & $2.17 \times 10^{-2}$ & --- \\ 
    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
                $1.25 \times 10^{-1}$ & 5.76 \\
    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
                $1.59 \times 10^{0}$ & 12.72 \\
    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
                $2.19 \times 10^{1}$ & 13.77 \\
    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
                $2.14 \times 10^{2}$ & 9.77 \\
    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
                $2.20 \times 10^{3}$ & 10.14 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
  inflating ($t_\mathrm{inflate}$).}
\end{table}

\begin{figure}[htp]
\centering
\ifTikz
\input{figures/ellipseArea.tikz}
\fi
  \caption{\label{fig:ellipseArea} The area of an elliptical
  semi-permeable vesicle, with permeability rate $\beta$ in a quiescent
  flow. The solid lines compute the area using
  equation~\eqref{eqn:area}, while the marks are computed by integrating
  equation~\eqref{eqn:areaROC}. The dashed black lines are the times
  when the vesicle's area is within 1.3\% of its maximum value of
  $4\pi$.}
\end{figure}

We further analyze the transient dynamics for small $\beta$ by
considering the vesicle velocity~\eqref{eqn:vesVelocity} due to
semi-permeability, $\beta(\ff \cdot \nn)\nn$, and force balance,
$\SS[\ff]$. Initially, since $\beta$ is small, the semi-permeability velocity is much
smaller than the balance velocity. Therefore,
the velocity resembles that of an impermeable vesicle. However, as the
vesicle approaches the steady state shape of an impermeable vesicle, the
force balance velocity decreases below the semi-permeability velocity,
at which point the semi-permeable vesicle begins to inflate.  Finally,
the vesicle semi-permeable inflates until it is circular with zero
membrane force, and therefore zero velocity.  Letting $\beta = 10^{-3}$,
in Figure~\ref{fig:vesVelocity} we plot the force balance velocity
(blue) and the semi-permeability velocity (red) at three times. We also
plot the velocity of an identically initialized impermeable vesicle
(green). At $t=0.5$, semi-permeability velocity is small relative to the
force balance velocity, and the semi-permeable velocity matches with the
impermeable vesicle velocity. At time $t=5$, the velocity of the
impermeable vesicle, and also the force balance velocity, are comparable
in size to the semi-permeability velocity, and the semi-permeable
vesicle begins to inflate. Then, at time $t=50$, the impermeable vesicle
is at its steady state, while the semi-permeable vesicle still has
contributions due to semi-permeability and force balance. In
Figure~\ref{fig:vesVelocityNorm}, we plot the maximum norm of the
different velocity contributions as a function of time. The black
vertical lines correspond to the times reported in
Figure~\ref{fig:vesVelocity}. Again, we see that the velocity of a
semi-permeable vesicle initially agrees with the velocity of an
impermeable vesicle. Then, as the force balance velocity approaches
zero, the semi-permeable velocity becomes significant, causing the
vesicle to inflate until it reaches a steady state circular shape.

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/ellipseVelocity1.tikz}
  \input{figures/ellipseVelocity2.tikz}
  \input{figures/ellipseVelocity3.tikz}
  \fi
  \caption{\label{fig:vesVelocity} The velocity contributions due to
  semi-permeability (red) and force balance (blue). The green dashed
  line is the velocity of an impermeable vesicle with the same initial
  shape as the semi-permeable vesicle.}
\end{figure}

@@

Finally, we consider a semi-permeable vesicle, with $\beta=1$, that
initially has regions with positive curvature and others with negative
curvature. The vesicle shape at several time steps is in
Figure~\ref{fig:starShape}, and, as we have shown, the steady state
shape is circular.  We also compute the tension, $\Lambda$, and the
flux, $\ff \cdot \nn$, and plot the results in
Figure~\ref{fig:starTensionFlux}. The vesicle undergoes three general
behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the vesicle has a net
negative flux resulting in a loss of area; (ii) For $t \in (1.6 \times
10^{-2},1.0)$, the vesicle has a net positive flux and the tension most
of the membrane is undergoing negative tension; (iii) For $t \in
(1.0,2.0)$, the vesicle is near its steady state and transitions to a
positive constant tension. In the first time interval, the vesicle
deflates. Near the points of largest negative curvature, there is a
large negative tension and large inflow (positive flux).
Correspondingly, near the points with largest positive curvature, there
is a small tension and outflow (negative flux). In the second time
interval, the tension is negative and the flux is positive nearly
everywhere. The regions with largest negative curvature correspond to
regions with largest negative tension and the most inflow. Finally, in
the last time interval, the tension transitions to a positive constant
function, the membrane force and flux transition to zero, resulting in a
steady state circular vesicle with positive constant tension.

\begin{figure}[htp]
    \ifTikz
    \input{figures/starRelaxation1.tikz}
    \quad
    \input{figures/starRelaxation2.tikz}
    \quad
    \input{figures/starRelaxation3.tikz}
    \quad
    \input{figures/starRelaxation4.tikz}
    \quad
    \input{figures/starRelaxation5.tikz}
    \fi
  \caption{\label{fig:starShape} An initially star-shaped semi-permeable
  vesicle in a quiescent flow with $\beta=1$. Note that the time steps
  are not equispaced.}
\end{figure}

@@

  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
  \includegraphics[width=0.19\textwidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
  flux (bottom) of the semi-permeable vesicle in a quiescent
  flow with $\beta=1$.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear Flow}
\begin{itemize}
  \item Mild dependence on initial shape

  \item Look at tank-treading angle, tank-trading speed, reduced area,
    absolute value of the permeable flux

  \item Max flux at the steady state as a function of beta and
    $\dot{\gamma}$

@@

We consider a semi-permeable vesicle in the shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$.  For a two-dimensional
impermeable vesicle, depending on the reduced area and viscosity
contrast, vesicles in a shear flow either tank tread or
tumble~\cite{fin-lam-sei-gom2008,kra-win-sei-lip1996}, but tumbling is
not possible with viscosity contrast of one. Since we are considering
semi-permeable vesicles, we assume that there is no viscosity contrast,
and we do not expect to observe tumbling dynamics.

We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
with its long axis oriented in the $y$-direction. For all permeability
rates and shear rates, the semi-permeable vesicle tilts to an
inclination angle and undergoes tank-treading behavior. However, because
of the semi-permeability, the final reduced area does not agree with the
initial reduced area. In Figure~\ref{fig:shearPhase}, we plot the final
shape of the vesicle for various permeability rates, $\beta$, and shear
rates $\dot{\gamma}$. We also includes lines of constant final reduced
area. We see that the shear rate has the largest effect on the final
reduced area. However, for small $\beta$, the permeability rate also has
a large effect on the final reduced area. In particular, the smallest
final reduced areas are the result of large shear rates and small
permeability rates.

\begin{figure}[htp]
\ifTikz
\input{figures/shearPhaseDiagram.tikz} 
\fi
  \caption{\label{fig:shearPhase} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
  contour lines of the final reduced areas, and the reduced area are
  reported on the right.}
\end{figure}
